\Large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-03 paper/main.tex
backing up progress:   - switched to updated version of quail to fix "all features have the same value" corrected clustering score edge case   - working on re-computing all fingerprints (this will take a few days to complete; only the first batch are included in this update)   - working on addressing reviewer 1 comments in the main text (not yet complete)

% connections to prior work: 
%     - context effects: role of irrelevant features, temporal context and order effects
%     - priming: being "primed" to 
%     - situation models:

>>>>

% connections to prior work: 
%     - richness of encoding
%     - context effects: role of irrelevant features, temporal context and order effects
%     - priming: being "primed" to 
%     - situation models:

\subsection*{Memory consequences of feature variability}

Several prior studies have examined how varying the richness or experiences, or
the extensive of encoding, can affect memory. Although specific details
differ~\citep{BoniEtal22}, in general these studies have found that richer and
more deeply or extensively encoded experiences are remembered
better~\citep{HargEtal12, Mada21, MeinEtal20}. Our findings help to elucidate
an additional factor that may contribute to these phenomenon. For example, our
finding that participants better remember ``feature rich'' lists (where words'
appearances are varied) than ``reduced'' lists (where words' appearances are
held constant) only when those feature rich lists are presented \textit{after}
reduced lists suggests that some factors that influence the richness or depth
of encoding may be relative, rather than absolute. In other words,
\textit{changes} in richness may be more important than the overall complexity
or numbers of features.

We did \textit{not} find any evidence that changing words' appearances
\textit{harmed} memory performance, e.g., by distracting them with irrelevant
information~\citep{MarsEtal15, Lang05, MarsEtal12, ReinEtal92}. Nor did we find
any evidence that \textit{changes} in the presence of potentially
``distracting'' features adversely affected memory. For example, when we
increased or decreased the variability in words' appearances on late versus
early lists (as in the reduced (early) and reduced (late) conditions), we found
no evidence that this harmed participants' memories.

% add something about multiple pathways to recall (for different feature dimensions)
